### 2014-10-21 paper/include/dtail.tex
git push hej

When a row is selected for refresh by the memory controller, DTail intercepts the refresh command and based on the Retention Time and Validity information, either lets the refresh to be performed or cancels it. The command used for refreshing a row depends on what is the most efficient at the time, if a large number of rows need refresh then CBR is selected, otherwise ROR is used. To be able to use CBR, Cui et al. proposes a new refresh command that increments a rank's internal address counter, which makes it possible for the internal address counter to be synchronized with MC's address counter.

>>>>

The number of rows refreshed when a CBR is issued is denoted by Cui et al. as a super row. When the first row in a super row is selected for refresh, DTail decides if CBR or ROR should be used for all the consecutive rows in the super row. If a large number of rows need to be refreshed then CBR is selected, otherwise ROR. To be able to use CBR, Cui et al. proposes a new refresh command that increments a rank's internal address counter, which makes it possible for the internal address counter to be synchronized with MC's address counter. When ROR is used, the row's Retention Time and Validity information is considered; if the row is valid and the time since the last refresh is $n \times 64\:ms$ a refresh is performed.
